\section{System Requirements}
\tpc{} requires a computer running a \textsf{Linux} operating system with a 3.x series kernel.
It has been tested on a system running Fedora 22 Linux distribution, more precisely \code{GNU/Linux 3.19.5-100.fc20.x86\_64}.
The recommended Linux distribution for the Xilinx Zynq platforms is \emph{archlinux/ARM} \cite{archlinuxarm}, which is also the basis for the ready-for-use SDcard image files available on the \tpc{} website.
No other system requirements have been identified for \tpc{}, however, the requirements of subsequently listed third-party software apply.

\section{Prerequisites}
\tpc{} is based on several third-party software components, the most important of which are listed in \tblref{tbl:thirdparty}.
If nothing else is explicitly specified in the corresponding section, C/C++ code can be built by the GNU project toolchain, specifically the GNU C Compiler gcc \cite{gcc} and GNU make \cite{gmake}, Scala code by the Scala compiler \cite{scala} and \gloss{sbt} \cite{sbt} (for supported versions see \tblref{tbl:thirdparty}).
It is likely possible to use different tools for these tasks, but is neither recommended nor supported.
\emph{Xilinx Vivado Design Suite} is used for all synthesis tasks, but the capabilities of the Vivado Simulator (specifically the SystemVerilog DPI implementation) are not sufficient for simulation, hence simulation is tailored toward \emph{Mentor Graphics ModelSim}.
With the exception of \gloss{sbt}, for which a micro-installation guide is provided in the next paragraph, a working installation of the software components is assumed.
Please refer to the corresponding vendor's documentation for installation instructions.

\begin{longtable}[c]{llcc}
  \caption{Third-party software components and compatible versions}
  \label{tbl:thirdparty}\\
  \toprule
  \textbf{Software Name} & \textbf{Vendor} & \textbf{Version} & \textbf{Mandatory}\\\midrule
  \endhead
  \bottomrule
  \endlastfoot
  gcc/g++ & Free Software Foundation, Inc. & $\geq$ 4.9 & Yes\\\midrule
  ModelSim SE & Mentor Graphics Corporation & $\geq$ 10.0c\_1 & No\\\midrule
  sbt & Typesafe, Inc. & $\geq$0.13.5 & Yes\\\midrule
  Scala & \begin{minipage}{5cm}Programming Methods Laboratory of École Polytechnique Fédérale de Lausanne\end{minipage} & 2.10 & Yes\\\midrule
  Vivado Design Suite & Xilinx, Inc. & 2015.2 & Yes\\
\end{longtable}

\subsection*{Installation of sbt}
In case no precompiled package for \gloss{sbt} is provided for your Linux distribution, a very simple manual installation of \gloss{sbt} is possible:

\begin{enumerate}
  \item Download a compatible version of \code{sbt-launch.jar} at\\
        \url{https://repo.typesafe.com/typesafe/ivy-releases/org.scala-sbt/sbt-launch/}.
  \item Put \code{sbt-launch.jar} in a directory in the \code{PATH} environment variable, e.g., \code{\textasciitilde/bin}, or adapt your \code{PATH} accordingly.
  \item At the same location, create a script \code{sbt}, with the following contents:
        \begin{lstlisting}[language=bash]
SBT_OPTS="-Xms512M -Xmx1536M -Xss1M -XX:+CMSClassUnloadingEnabled \
  -XX:MaxPermSize=256M"
java $SBT_OPTS -jar `dirname $0`/sbt-launch.jar "$@"
	\end{lstlisting}
\end{enumerate}

Check if the installation was successful by running \code{sbt version} on a command line, it should finish without errors.
For more information about \gloss{sbt}, refer to \cite{sbt}.

\section{Paths and other preparations}
Make sure that all software components listed in \tblref{tbl:thirdparty} are accessible from the command line.
If necessary, add their location to the \code{PATH} environment variable or source appropriate scripts supplied by the vendor.
To check this, make sure you can run the following commands from the command line:

\begin{lstlisting}[language=bash, breaklines=true]
~$ echo exit | vivado_hls -i
~$ echo exit | vivado -nojournal -nolog -mode tcl 
~$ echo quit | vsim -c
~$ gcc -v
~$ sbt version
\end{lstlisting}

Running the commands should yield output similar to this:
\begin{lstlisting}[language=bash, breaklines=true]
~$ echo exit | vivado_hls -i
================================================================
  Vivado(TM) HLS - High-Level Synthesis from C, C++ and SystemC
  Version 2015.2
  Build 1266856 on Fri Jun 26 16:57:37 PM 2015
  Copyright (C) 2015 Xilinx Inc. All rights reserved.
================================================================
@I [LIC-101] Checked out feature [VIVADO_HLS]
@I [HLS-10] Running '/opt/cad/xilinx/vivado/Vivado_HLS/2015.2/bin/unwrapped/lnx64.o/vivado_hls'
            for user 'jk' on host 'mountdoom.esa.informatik.tu-darmstadt.de' (Linux_x86_64 version 3.19.5-100.fc20.x86_64) on Mon Nov 02 11:05:24 CET 2015
            in directory '/home/jk/rcu/doc'
@E [HLS-70] There is an error calling 'vivado_hls'; try "-help'.
@I [LIC-101] Checked in feature [VIVADO_HLS]
================================================================
  Vivado(TM) HLS - High-Level Synthesis from C, C++ and SystemC
  Version 2014.3
  Build 1034051 on Fri Oct 03 16:32:44 PM 2014
  Copyright (C) 2014 Xilinx Inc. All rights reserved.
================================================================
@I [LIC-101] Checked out feature [VIVADO_HLS]
@I [HLS-10] Running '/opt/cad/xilinx/vivado/Vivado_HLS/2014.3/bin/unwrapped/lnx64.o/vivado_hls'
            for user 'jk' on host 'mountdoom.esa.informatik.tu-darmstadt.de' (Linux_x86_64 version 3.17.8-200.fc20.x86_64) on Tue Feb 10 17:28:49 CET 2015
            in directory '/home/jk'
@E [HLS-70] There is an error calling 'vivado_hls'; try "-help'.
@I [LIC-101] Checked in feature [VIVADO_HLS]
~ $ echo exit | vivado -nojournal -nolog -mode tcl 
****** Vivado v2015.2 (64-bit)
  **** SW Build 1266856 on Fri Jun 26 16:35:25 MDT 2015
  **** IP Build 1264090 on Wed Jun 24 14:22:01 MDT 2015
    ** Copyright 1986-2015 Xilinx, Inc. All Rights Reserved.

exit
INFO: [Common 17-206] Exiting Vivado at Mon Nov  2 11:06:22 2015...
~$ echo quit | vsim -c
Reading /opt/cad/mentor/modelsim/modelsim-10.0c_1/modeltech/tcl/vsim/pref.tcl 

# 10.0c_1

#  
ModelSim> quit
~$ gcc -v
Using built-in specs.
COLLECT_GCC=gcc
COLLECT_LTO_WRAPPER=/usr/local/libexec/gcc/x86_64-unknown-linux-gnu/5.2.0/lto-wrapper
Target: x86_64-unknown-linux-gnu
Configured with: ../5.2.0/configure
Thread model: posix
gcc version 5.2.0 (GCC)
~$ sbt version

[info] Set current project to jk (in build file:/home/jk/)
[info] 0.1-SNAPSHOT
~$
\end{lstlisting}

\input{ig_compile_simlib.tex}
\input{ig_installation.tex}
